A Comparison of Graph Processing Systems

### 2020-09-18 documentation/paper/sections/results/sssp.tex
kleine änderungen von Rückmeldung 3 in den sssp results, todo sind noch die result-Überschriften

\subsection{Single-source Shortest-paths}
For the results of our SSSP runs, we first analyze the single-node and distributed performances separately before comparing the two.

\subsubsection{Single-node}
\begin{figure*}
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_calcTime.png}
		\caption{Calculation times}
		\label{fig:singleNodeSSSP_calc}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_execTime.png}
		\caption{Execution times}
		\label{fig:singleNodeSSSP_exec}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_overheadTime.png}
		\caption{Overhead time}
		\label{fig:singleNodeSSSP_overhead}
	\end{subfigure}
	\caption{Average times for SSSP on a single computation node, black bars represent one standard deviation in our testing.}
	\label{fig:singleNodeSSSP}
\end{figure*}
Beginning with the single-node performance, \autoref{fig:singleNodeSSSP} shows the average calculation and execution times for SSSP on the different frameworks.
Note, that Giraph ran out of memory ($>$250 GB) for all graphs larger than wikipedia (twitter, rMat27, friendster and rMat28). Thus, the data points on the larger graphs for Giraph are missing in the figures and our evaluation. 
Also, both Ligra and Polymer failed on rMat28. Because of that, removed rMat28 in this section.

@@

Comparing the other frameworks (i.e. excluding Giraph in the further comparisons), shows them to perform similar on the smaller graphs. There, the average calculation times of the four frameworks (Galois, Gemini, Ligra, Polymer) are 35ms on flickr, 77ms on orkut, 538ms on wikipedia. 
The four frameworks are close to this average for the smaller graphs. Galois and Gemini being 24ms and 12ms faster than the average. Ligra and Polymer are slower by 27ms and 9ms.
Orkut is the graph where all the four frameworks are within 20ms of their average, Galois being the outlier at 19ms slower than average.
For wikipedia, Galois and Ligra are close to each other, while Gemini is 560ms (104\%) slower than the average of the four frameworks.
And Polymer is the fastest framework on wikipedia, being 330ms (61\%) faster than the others.
For the larger graphs, Polymer has the shortest computation time as well. Gemini is second, taking about 1.9$\times$ times the computation time of Polymer on twitter and friendster while being equally fast (8\% longer) on rMat27. Galois and Ligra however have much longer computation times compared to Polymer. Galois takes anywhere from 3.3$\times$ (twitter) to 4.2$\times$ (friendster) the computation time of Polymer.
Ligra requires between 3.2$\times$ (friendster) and 9.8$\times$ (twitter) the computation time of Polymer on the larger graphs. This makes Ligra the slowest Framework on both twitter and rMat27. Galois is the slowest on friendster.
However, while especially Galois is comparably slow to Polymer in the computation time, it is important to keep in mind that Polymer could not finish computation on rMat28. Meanwhile both Gemini and Galois managed just fine.

>>>>

\subsection{Single-Source Shortest-Paths}
In this section, we compare the different frameworks in their performance on the SSSP algorithm. We first analyze the frameworks on a single computation node and compare to the distributed setup after that.
\subsubsection{Single-node}
\begin{figure*}
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_calcTime.png}
		\caption{Calculation times}
		\label{fig:singleNodeSSSP_calc}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_execTime.png}
		\caption{Execution times}
		\label{fig:singleNodeSSSP_exec}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_overheadTime.png}
		\caption{Overhead time}
		\label{fig:singleNodeSSSP_overhead}
	\end{subfigure}
	\caption{Average times for SSSP on a single computation node, black bars represent one standard deviation in our testing.}
	\label{fig:singleNodeSSSP}
\end{figure*}
Beginning with the single-node performance, \autoref{fig:singleNodeSSSP} shows the average calculation and execution times for SSSP on the different frameworks.
Note, that Giraph ran out of memory ($>$250 GB) for all graphs larger than wikipedia (twitter, rMat27, friendster and rMat28). Thus, the data points on the larger graphs for Giraph are missing in the figures and our evaluation. 
Also, both Ligra and Polymer failed on rMat28.

@@

Comparing the other frameworks (i.e. excluding Giraph in the further comparisons), shows them to perform similar on the smaller graphs. There, the average calculation times of the four frameworks (Galois, Gemini, Ligra, Polymer) are 35ms on flickr, 77ms on orkut and 538ms on wikipedia. 
The four frameworks are close to this average for the smaller graphs. Galois and Gemini being 24ms and 12ms faster than the average. Ligra and Polymer are slower by 27ms and 9ms.
Orkut is the graph where all the four frameworks are within 20ms of their average, Galois being the outlier at 19ms slower than average.
For wikipedia, Galois and Ligra are close to each other, while Gemini is 560ms (104\%) slower than the average of the four frameworks.
And Polymer is the fastest framework on wikipedia, being 330ms (61\%) faster than the others.
For the larger graphs, Polymer has the shortest computation time as well. Gemini is second, taking about 1.9$\times$ times the computation time of Polymer on twitter and friendster while being equally fast (8\% longer) on rMat27. Galois and Ligra however have much longer computation times compared to Polymer. Galois takes anywhere from 3.3$\times$ (twitter) to 4.2$\times$ (friendster) the computation time of Polymer.
Ligra requires between 3.2$\times$ (friendster) and 9.8$\times$ (twitter) the computation time of Polymer on the larger graphs. This makes Ligra the slowest Framework on both twitter and rMat27. Galois is the slowest on friendster.
However, while especially Galois is comparably slow to Polymer in the computation time, it is important to keep in mind that Polymer could not finish computation on rMat28. Meanwhile both Gemini and Galois managed just fine.
